%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.3 in,top=0.08 in,right=0.3 in,bottom=0.35 in]{geometry} % Document margins
\usepackage{url}
\usepackage{hyperref}
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor   = blue %Colour of citations, could be ``red''
}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Karan Sharma} % Your name
\address{352-328-7913 \\  1400 Spring Garden Street, Philadelphia - PA} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{\url{sharma.karan9341@gmail.com} \\ \url{https://www.linkedin.com/in/
ksh24
} \\  \url{https://www.github.com/karansharmaufl}/ }  % Your phone number and email


\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

%\begin{rSection}{OBJECTIVE}

%{Recently graduated, multidisciplinary Engineer with excellent problem solving abilities and process-thinking skill seeks hands on experience within a company that embraces creativity and innovation.Through my studies, I have gained extensive knowledge of production and manufacturing engineering, product design, among many other components of  Mechanical Engineering.Effective communicator who builds positive, cohesive relationship with all level of staff, eager to put my extensive studies to practical, applied use.}%


%\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Master of Science in Computer Science } \hfill {Dec 2017}
\\ 
University of Florida, Gainesville, FL 
\\
{\bf Bachelor of Technology in Computer Science and Engineering} \hfill {June 2016}
\\
Jaypee University Of Information Technology, Solan, India  
\end{rSection}




\begin{rSection}{Coursework}

{\bf Graduate}: Principals of Programming Languages, Pattern Recognition, Computer Networks, Advanced Data Structures, Analysis of Algorithms 
\\ 
{\bf Undergraduate}: Object Oriented Programming, Database Management System, Operating Systems
\end{rSection}



%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
%\begin{rSection}{Coursework}
%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Graduate&Principal of Programming Languages, Pattern Recognition, Computer Networks, \\& Advanced Data %Structures, Analysis of Algorithms \\
%UnderGraduate&Object Oriented Programming,Database Management System, Operating Systems, Mobile %Computing
%\end{tabular}
%\end{rSection}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{work EXPERIENCE}


\begin{rSubsection}{Data Scientist}{April 2019 - Present} {Black Knight Financial Services $|$ Philadelphia, USA} {}
\item Currently working on a \textbf{\textit{Correspondent System}} for Banks built using state of the art modern day technologies like \textbf{\textit{Cloud Computing, AI, Distributed Systems}}.
\item Developed numerous micro-services using \textbf{\textit{AWS Lambda, API Gateway, Cloud Formation templates}} and consumed them in a front end application written in \textbf{\textit{Angular7}}
\item Worked on \textbf{\textit{migrating EC2 server logs}} to centralized log repository \textbf{\textit{Cloudwatch}}.
\end{rSubsection}


\begin{rSubsection}{Software Engineer Intern}{Jan 2019 - March 2019} {Black Knight Financial Services $|$ Philadelphia, USA} {}
\item Created a POC service for building code(Java, Python, Node) using \textbf{\textit{AWS Codebuild, Lambda, APIGateway.}}
\item Performed load testing on existing microservices using \textbf{\textit{AWS Sagemaker}}.
\item Contributed to existing \textbf{\textit{continuous integration}} pipelines built on Jenkins by extending downstream jobs thereby increasing automation.
\end{rSubsection}

\begin{rSubsection}{Software Developer Intern}{May 2018 - Jan 2019} {Genesis Global Technologies $|$ Fort Myers, USA} {}
\item Developed a \textbf{\textit{Geographical Mapping System}} using OpenLayers, used extensively for geocoding contact data.
\item Worked in a team to identify and resolve bottlenecks causing timeout issues during content loading in ABBI. 
\item Developed a \textbf{\textit{Object Oriented Data Visualisation System}} using c\#, d3.js and SQL to render Bar Graphs, Pie Charts, Line Charts etc used for data visualization throughout the application.
\item Developed a subscribe and go page for creating new subscriptions. Integrated the application with Authorize.NET a restful API used for payment processing.
\end{rSubsection}


\end{rSection}


\begin{rSection}{Projects}


\begin{rSubsection}{Document Classification, Machine Learning | Python}{Nov 2018}{}

\item Developed and deployed a serverless machine learning model for classifying text documents. Used AWS Lambda with API Gateway for HTTP endpoint. 
\end{rSubsection} 


\begin{rSubsection}{Distributed Operating Systems Projects | Elixir} {Aug 2017 - Dec 2017}{}

\item Worked in a team of two and implemented distributed architecture projects for Bitcoin Miner, Gossip Simulator, Pastry Protocol and Twitter Simulator Engine. 
\end{rSubsection} 



\begin{rSubsection}{Image Processing Compiler | Java} {Aug 2017 - Dec 2017}{}

\item Implemented an image processing compiler (in Java) using core Java and ASM which is an open source Assembly Language
Library for JVM. 
\item Used the visitor design pattern for an object oriented approach. Wrote a test suite on JUnit for test driven development and white box testing.
\end{rSubsection} 


\end{rSection} 


\begin{rSection}{TECHNICAL SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Domains& Cloud Computing, Full Stack Application Development, Business Intelligence, Machine Learning \\
Languages&Java,  Python, Shell Scripting, JavaScript, TypeScript  \\
Database& SQL Server, DaynamoDB\\
Tools& GITHUB, Eclipse, Visual Studio, Lucid Charts \\

\end{tabular}
\end{rSection}


\end{document}
